\documentclass[10pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.06cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \textbf{Nguyen Huu Hoang Minh}\\ 
    \hrulefill
\end{center}

\begin{center}
    Ho Chi Minh City \textbullet \ nhhminh.2004.work@gmail.com \textbullet \ +84949916403 \textbullet \ \url{https://nguyenhuuhoangminh.me/}
\end{center}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{University of Science, VNU-HCM} \hfill Ho Chi Minh City, Vietnam

Bachelor, Advanced Program in Computer Science (APCS). GPA: 3.90 / 4.0 \hfill 2022-Now

\begin{center}
    \textbf{Skills}
\end{center}

\textbf{Programming Languages}: Java, C++, Python, JavaScript, PHP, Go

\textbf{Frameworks}: Spring, Node.js, React.js, Express.js

\textbf{Databases}: MySQL, MongoDB

\textbf{DevOps}: Git, GitHub Actions, CI/CD, Docker, RabbitMQ

\textbf{Others}: System Design, OOP, Computer Vision, Machine Learning

\textbf{Languages}: Vietnamese (Native), English

\begin{center}
    \textbf{Experience}
\end{center}

\textbf{ZALORA Group} \hfill Ho Chi Minh City, Vietnam

\textbf{Software Engineer Intern} \hfill Aug 2025 - Feb 2026

\textbf{Technologies}: PHP, Golang, GitHub Actions, RabbitMQ, Prometheus, n8n
\begin{itemize}[nosep, leftmargin=*]
    \item Spearheaded CI/CD migration from Jenkins/CircleCI to GitHub Actions, reducing build time and cost while streamlining deployment workflow.
    \item Elevated code quality by enforcing PHPStan Level 1 standards and increasing Integration Test coverage to 34\%.
    \item Architected and maintained RabbitMQ infrastructure for high-availability asynchronous microservices communication.
    \item Revamped monitoring stack by migrating from Graphite to Prometheus, enabling granular metrics and accurate alerting.
    \item Standardized payment log storage across all payment methods, reducing payment issue investigation time by 70\%.
    \item Designed automated workflows with n8n for Customer Service team, reducing manual workload and response times.
    \item Conducted R\&D on FrankenPHP as a replacement for PHP-FPM, delivering a Proof of Concept and benchmarks that demonstrated significant performance improvements.
\end{itemize}

\vspace{4pt}

\textbf{GihOt Studio} \hfill Ho Chi Minh City, Vietnam

\textbf{Game Back-End Developer Intern} \hfill Jun 2025 - Aug 2025

\textbf{Technologies}: Java 17, Spring Boot, MongoDB, Netty, WebSocket
\begin{itemize}[nosep, leftmargin=*]
    \item Designed and implemented the entire game-server stack for a real-time multiplayer title blending MOBA, RTS and minion-control mechanics.
    \item Built RESTful microservices with Spring Boot for authentication, matchmaking, and room/lobby management; persisted data in MongoDB.
    \item Developed a low-latency Netty-powered WebSocket gateway with custom TLV binary protocol for streaming gameplay events.
    \item Implemented game logic including position synchronization, combat mechanics, and skill-casting systems for scalable server-side processing.
    \item Deployed and maintained game services on VPS infrastructure with monitoring, achieving 99\% uptime.
\end{itemize}

\begin{center}
    \textbf{Projects}
\end{center}

\textbf{Clothing \& Lifestyle E-commerce Platform} \hfill May 2025 - Present

\textbf{Technologies}: React, TailwindCSS, Node.js, Express, MongoDB
\begin{itemize}[nosep, leftmargin=*]
    \item Built a full-stack e-commerce application with React frontend and Express/Node.js REST API backend.
    \item Implemented user authentication, product catalog, shopping cart, and order management features.
\end{itemize}
\textbf{GitHub}: \url{https://github.com/orgs/AodaimaysanDev/repositories} | \textbf{Live}: \url{https://aodaimaysancodinh.netlify.app/}

\begin{center}
    \textbf{Publications}
\end{center}
\textbf{AI-Generated Image Recognition via Fusion of CNNs and Vision Transformers} \hfill Sept 2024 - Dec 2024

Xuan-Bach Mai, Hoang-Minh Nguyen Huu, Quoc-Nghia Nguyen, Hoang-Tung Vu, Minh-Triet Tran, Trung-Nghia Le

Proceedings of the 13th International Symposium on Information and Communication Technology (SOICT 2024), CCIS Volume

\textbf{Springer}: \url{https://link.springer.com/chapter/10.1007/978-981-96-4282-3_6}

\begin{center}
    \textbf{Awards}
\end{center}
\textbf{Second prize} - Kien Giang Olympiad in Informatics - 2021

\textbf{Consolation prize} - Vietnam Olympiad in Informatics - 2022

\textbf{Vallet Scholarship 2022} - Rencontres du Vietnam and Professor Odon Vallet

\textbf{First prize} - ICPC University Round - 2022 - Team \textbf{HCMUS-Potatoes}

\textbf{Co-second prize} - ICPC Asia Ho Chi Minh City Regional Contest - 2022 - Team \textbf{HCMUS-Potatoes}

\end{document}
